The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-02-11 paper.tex
Just before tackling the Results section

SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic Star Formation Rate Density (SFRD) \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
There is also an increasing body of work measuring the relationship between the observed maximum rotational velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Tiley2016a,Harrison2017}.
In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.

@@

This study focusses on the final question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotational velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS we have been able to spatially resolve [O~{\sc III}]$\lambda$5007 emission in 44 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.

The structure of the paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:extracting_properties} we explain how two-dimensional maps of physical properties were extracted from our stacked datacubes and the treatment of the HST imaging to derive the morphological properties of our galaxies.
We also define a classification procedure which separates the KDS galaxies into a merger and modelling sample.
In \cref{sec:Kinematic_Properties} we present the kinematic modelling applied to the KDS galaxies, including the beam smearing correction, and the method chosen to extract the kinematic properties following this modelling procedure.
\cref{sec:results} presents an analysis of the derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
We present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

@@

 \hline
Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band(s) & Exp. Time (ks) & Seeing ($^{\prime\prime}$)  \\
 \hline
 GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & 2 & 17 & K, H & 32.4 & 0.50 \\
GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 19 & K, H & 31.8 & 0.52 \\
SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & 1 & 9 & HK & 27.8 & 0.57 \\
SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 10 & 46 & 8 & 80 & HK & 38.1 & 0.62 \\
 \hline
\end{tabular}
\begin{tablenotes}
      \small
      \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{Physical properties of the KDS field galaxies as measured from SED fitting and from applying GALFIT \protect\citep{Peng2010_galfit}}
\label{tab:phys-props}
\begin{tabular}{ccccccccccc}

@@

 GOODS-S & & & & & & & & & & \\

@@

 SSA22 & & & & & & & & & & \\

@@

lab7\_top     & 22:17:41 & +00:11:28 & 3.095      & 23.8919 & 9.89  & -            & 0.51        & 61.0        & 139.0   & 1.47 \\

@@

\subsection{Morphological Measurements}
For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high resolution photometry.
This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies and helps to distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
In the following sections we describe the approach we have chosen to recover these parameters.
In section \cref{subsubsection:morph_param_summary} we compare the KDS morphological parameters with those described in \cite{VanderWel2012}, and also with spectroscopically confirmed galaxies in different redshift intervals in order to study the size evolution of SFGs across cosmic time.

@@

We first run SExtractor \citep{Bertin1996} across the full fields to recover initial input parameters and segmentation maps for running GALFIT, and then extract postage stamp regions around the galaxies in the KDS sample.
At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.
This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012} (with the median ratio of $\chi ^{2}$ values equal unity in all cases). Additionally, for the corresponding objects in the \cite{VanderWel2012} catalogue the median \Sers index value is 1.2.
The use of exponential profiles also facilitates comparison with recent large surveys such as KROSS \citep{Harrison2017}, in which beam smearing correction factors are applied to the derived kinematic parameters as function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:param_extraction}), and KMOS$^{3D}$ \citep{Wisnioski2015}.

@@

\subsubsection{Half-light radii}\label{subsubsection:half-light_radii}
The third morphological parameter is the half-light radius, $R_{1/2}$, which provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
As discussed throughout the introduction and in \cref{subsubsec:param_extraction}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
Knowledge of $R_{1/2}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made, both of which are important when making comparisons to previous IFU studies \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d modelling}), which requires the $R_{1/2}$ value for each galaxy.
A final use of the derived $R_{1/2}$ values is to verify our beam smearing correction results through comparison with systematic correction factors presented in Johnson et al. (in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:param_extraction}).

@@

We proceed now to extract 2D measurements from the KDS datacubes by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
We then describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam smearing corrections for each galaxy.

@@

\subsubsection{3D modelling and beam smearing corrections}\label{subsec:3d_modelling}

@@

In this analysis we minimise the number of fitted parameters by making use of information from HST imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.    
We seek also to clearly distinguish between observed velocities and those inferred from modelling.
This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.  
There are thus two clear reasons for constructing model velocity fields; the first is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the second is to estimate the effect of beam smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.

@@

\noindent
with `r' measured as the distance from the centre of rotation, (xcen, ycen).
This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam smearing.
The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in section \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.

@@

Following the construction of a convolved cube and the measurement of the beam-smeared maps we can extract beam smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
We provide an overview of these surveys in section \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of the parameters used for comparison to the KDS throughout results section \cref{subsec:redshift_evolution}).

\subsubsection{KDS beam smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
We extract $V_{smeared}$ and $V_{C}$ by reading off from the beam-smeared and intrinsic best fitting 2D model grids respectively at $2R_{1/2}$.
The $R_{1/2}$ value used to extract velocities from the KMOS data is found by convolving the intrinsic $R_{1/2}$ value with the PSF of the observations.
The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
The beam smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in section \cref{subsubsec:observed_and_intrinsic}.
The $V_{C}$ errors are discussed in \cref{appsubsubsec:model_errors}.

In most of the KDS field sample galaxies, the $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, with 2 galaxies requiring extrapolation > 0.4$^{\prime\prime}$ with a mean extrapolation of 0.17$^{\prime\prime}$.
This extrapolation is a requirement imposed by the low S/N at the outskirts of the KDS galaxies, limiting the extent to which the ionised gas disk can be observed, with the majority of the observed velocity curves not reaching the point of flattening. 
The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radius marked on each velocity thumbnail.
We present the maximum observed velocity values, $V_{obs}$, and the intrinsic, inclination and beam smearing corrected model velocity values, $V_{C}$, in table \ref{tab:kin_props}.

\subsubsection{KDS beam smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
Convolution of the model velocity field with the seeing profile produces a peak in the beam-smeared velocity dispersion map at the centre of rotation.
The model therefore provides a beam smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the beam-smeared dispersion i.e. $\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
This is computed for each spaxel to provide the 2D $\sigma_{bs}$ correction map.
The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in section \cref{appsubsubsec:model_errors}.
We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.

To measure the $\sigma_{int}$ value for each galaxy in our sample we first use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the K-band and 55.4kms$^{-1}$ in the HK-band).
This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam smearing correction best recovers the $\sigma_{int}$ values.

@@

The median value of this map is taken as the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value, with both of these presented in table \ref{tab:kin_props}.

The beam smearing correction factor is then given by the ratio of these two medians, i.e. $\sigma_{obs}/\sigma_{int}$, with mean and median values of 0.77 and 0.79 respectively for the morphologically isolated KDS galaxies.

To test the robustness of our beam smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{d}/R_{psf}$, detailed in Johnson et al. (in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
These correction factors are applied to $V_{smeared}$ to reach $V_{C}$ and to $\sigma_{obs}$ to reach $\sigma_{int}$.
The $V_{C}$ values agree to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities. 
This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Dynamical Properties}
\label{tab:kin_props}
\begin{tabular}{cccccccc}

@@

ID & $V_{obs}$(kms$^{-1}$) & $V_{C}$(kms$^{-1}$) & $\sigma_{obs}$(kms$^{-1}$) & $\sigma_{int}$(kms$^{-1}$) & $V_{C}/\sigma_{int}$ & $R_{1/2}$(kpc) & PA$_{kin}^{\circ}$ \\

@@

 GOODS-S & & & & & & & \\
bs009818        & 65.0                    & 84.0                     & 95.0                  & 79.0                   & 1.06       & 1.25        & 72.0 \\
bs014828        & 32.0                    & 46.0                     & 97.0                  & 88.0                   & 0.53       & 1.65      & 44.0   \\
lbg\_20         & 26.0                    & 56.0                     & 55.0                  & 40.0                   & 1.39      & 1.30        & 41.0  \\
lbg\_105        & 13.0                    & 32.0                     & 68.0                  & 59.0                   & 0.54       & 1.75       & 170.0 \\
bs006541        & 36.0                    & 65.0                     & 96.0                  & 83.0                   & 0.78        & 1.85       & 23.0 \\
b012141\_012208 & 34.0                    & 93.0                     & 94.0                  & 63.0                   & 1.47       & 1.60       & 122.0 \\
b15573          & 62.0                    & 81.0                     & 111.0                 & 84.0                   & 0.97        & 0.50       & 118.0 \\

>>>>

SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic Star Formation Rate Density (SFRD) \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
There is also an increasing body of work measuring the relationship between the observed maximum rotational velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Tiley2016a,Harrison2017}.
In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.

@@

This study focusses on the final question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotational velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS we have been able to spatially resolve [O~{\sc III}]$\lambda$5007 emission in 43 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.

The structure of the paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:extracting_properties} we explain how two-dimensional maps of physical properties were extracted from our stacked datacubes and the treatment of the HST imaging to derive the morphological properties of our galaxies.
We also define a classification procedure which separates the KDS galaxies into a merger and modelling sample.
In \cref{sec:Kinematic_Properties} we present the kinematic modelling applied to the KDS galaxies, including the beam-smearing correction, and the method chosen to extract the kinematic properties following this modelling procedure.
\cref{sec:results} presents an analysis of the derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
We present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

@@

 \hline
Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band(s) & Exp. Time (ks) & Seeing ($^{\prime\prime}$)  \\
 \hline
 GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & 2 & 17 & K, H & 32.4 & 0.50 \\
GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 18 & K, H & 31.8 & 0.52 \\
SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & 2 & 18 & HK & 27.8 & 0.57 \\
SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
 \hline
\end{tabular}
\begin{tablenotes}
      \small
      \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying GALFIT \protect\citep{Peng2010_galfit}}
\label{tab:phys-props}
\begin{tabular}{ccccccccccc}

@@

@@

@@

@@

\subsection{Morphological Measurements}
For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution photometry.
This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies and helps to distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
In the following sections we describe the approach we have chosen to recover these parameters.
In section \cref{subsubsection:morph_param_summary} we compare the KDS morphological parameters with those described in \cite{VanderWel2012}, and also with spectroscopically confirmed galaxies in different redshift intervals in order to study the size evolution of SFGs across cosmic time.

@@

We first run SExtractor \citep{Bertin1996} across the full fields to recover initial input parameters and segmentation maps for running GALFIT, and then extract postage stamp regions around the galaxies in the KDS sample.
At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.
This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012} (with the median ratio of $\chi ^{2}$ values equal unity in all cases). Additionally, for the corresponding objects in the \cite{VanderWel2012} catalogue the median \Sers index value is 1.2.
The use of exponential profiles also facilitates comparison with recent large surveys such as KROSS \citep{Harrison2017}, in which beam-smearing correction factors are applied to the derived kinematic parameters as function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsubsec:param_extraction}), and KMOS$^{3D}$ \citep{Wisnioski2015}.

@@

\subsubsection{Half-light radii}\label{subsubsection:half-light_radii}
The third morphological parameter is the half-light radius, $R_{1/2}$, which provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
As discussed throughout the introduction and in \cref{subsubsec:param_extraction}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
Knowledge of $R_{1/2}$ gives a fixed point of extrapolation and a clear measure of how far beyond the data this extrapolation is made, both of which are important when making comparisons to previous IFU studies \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
Throughout our dynamical modelling section we will assume a flux profile when constructing mock datacubes (see \cref{subsec:3d modelling}), which requires the $R_{1/2}$ value for each galaxy.
A final use of the derived $R_{1/2}$ values is to verify our beam-smearing correction results through comparison with systematic correction factors presented in Johnson et al. (in prep), which are a function $R_{d} / R_{PSF}$ (see \cref{subsubsec:param_extraction}).

@@

We proceed now to extract 2D measurements from the KDS datacubes by fitting the [O~{\sc III}]$\lambda$5007 emission line profiles within individual spaxels.
We then describe our dynamical modelling and the approach we have followed to extract $V_{C}$ and $\sigma_{int}$, using the models to derive beam-smearing corrections for each galaxy.

@@

\subsubsection{3D modelling and beam-smearing corrections}\label{subsec:3d_modelling}

@@

In this analysis we minimise the number of fitted parameters by making use of information from HST imaging and by assuming a fixed function to describe the rotation curves as described in the following subsection.    
We seek also to clearly distinguish between observed velocities and those inferred from modelling.
This is particularly important when dealing with galaxies at $z > 3$, since we often do not have enough S/N away from the centre of the galaxy to observe the flattening of the rotation curve, consequently requiring extrapolation to determine $V_{C}$.  
There are thus two clear reasons for constructing model velocity fields; the first is to extrapolate the observations smoothly to some fiducial radius from which $V_{C}$ can be extracted; the second is to estimate the effect of beam-smearing on both the velocity and velocity dispersion fields so that we recover the set of intrinsic galaxy parameters which best describe the observations.
The following section describes our 3D modelling procedure, and the validation of our results through comparison with the techniques used to determine the dynamical properties presented in \cite{Harrison2017}.

@@

\noindent
with `r' measured as the distance from the centre of rotation, (xcen, ycen).
This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam-smearing.
The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in section \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.

@@

Following the construction of a convolved cube and the measurement of the beam-smeared maps we can extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
We provide an overview of these surveys in section \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of the parameters used for comparison to the KDS throughout results section \cref{subsec:redshift_evolution}).

\subsubsection{KDS beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
We extract $V_{smeared}$ and $V_{C}$ by reading off from the beam-smeared and intrinsic best fitting 2D model grids respectively at $2R_{1/2}$.
The $R_{1/2}$ value used to extract velocities from the KMOS data is found by convolving the intrinsic $R_{1/2}$ value with the PSF of the observations.
The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
The beam-smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in section \cref{subsubsec:observed_and_intrinsic}.
The $V_{C}$ errors are discussed in \cref{appsubsubsec:model_errors}.

In most of the KDS field sample galaxies, the $2R_{1/2}$ fiducial radius used to extract $V_{C}$ from the model is greater than the last observed radius, with 2 galaxies requiring extrapolation > 0.4$^{\prime\prime}$ with a mean extrapolation of 0.17$^{\prime\prime}$.
This extrapolation is a requirement imposed by the low S/N at the outskirts of the KDS galaxies, limiting the extent to which the ionised gas disk can be observed, with the majority of the observed velocity curves not reaching the point of flattening. 
The extent of the extrapolation for each galaxy is made clear throughout the kinematics plots in \cref{app:kinematics_plots}, with the $V_{C}$ extraction radius marked on each velocity thumbnail.

\subsubsection{KDS beam-smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
Convolution of the model velocity field with the seeing profile produces a peak in the beam-smeared velocity dispersion map at the centre of rotation.
The model therefore provides a beam-smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the beam-smeared dispersion i.e. $\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
This is computed for each spaxel to provide the 2D $\sigma_{bs}$ correction map.
The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in section \cref{appsubsubsec:model_errors}.
We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.

To measure the $\sigma_{int}$ value for each galaxy in our sample we first use equation \ref{eq:owen_sigma} to derive an intrinsic sigma map, where $\sigma_{inst}$ is a measure of the KMOS instrumental resolution value averaged across gaussian fits to several skylines (equal to 31.1kms$^{-1}$ in the K-band and 55.4kms$^{-1}$ in the HK-band).
This follows the approach of \cite{Stott2016} which shows that linear subtraction of the beam-smearing correction best recovers the $\sigma_{int}$ values.

@@

The median value of this map is taken as the $\sigma_{int}$ value for that galaxy and the median value of the observed map is the $\sigma_{obs}$ value.
The beam-smearing correction factor is then given by the ratio of these two medians, i.e. $\sigma_{obs}/\sigma_{int}$, with mean and median values of 0.77 and 0.79 respectively for the morphologically isolated KDS galaxies.

To test the robustness of our beam-smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{d}/R_{psf}$, detailed in Johnson et al. (in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
These correction factors are applied to $V_{smeared}$ to reach $V_{C}$ and to $\sigma_{obs}$ to reach $\sigma_{int}$.
The $V_{C}$ values agree to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities. 
This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.

We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for all of the spatially resolved KDS field galaxies classified as morphologically isolated (29, see section \cref{subsec:morpho-kin-class}).

\begin{table*}
\centering
\begin{threeparttable}
\caption{Dynamical Properties for the resolved and morphologically isolated KDS field galaxies}
\label{tab:kin_props}
\begin{tabular}{ccccccccc}

@@

ID & $V_{obs}$(kms$^{-1}$) & $V_{C}$(kms$^{-1}$) & $\sigma_{obs}$(kms$^{-1}$) & $\sigma_{int}$(kms$^{-1}$) & $V_{C}/\sigma_{int}$ & $R_{1/2}$(kpc) & PA$_{kin}^{\circ}$ & Class$^{a}$ \\

@@

bs009818        & 65.0                    & 84.0                     & 95.0                  & 79.0                   & 1.06       & 1.25        & 72.0 & RD \\
bs014828        & 32.0                    & 46.0                     & 97.0                  & 88.0                   & 0.53       & 1.65      & 44.0 & DD    \\
lbg\_20         & 26.0                    & 56.0                     & 55.0                  & 40.0                   & 1.39      & 1.30        & 41.0 & RD  \\
lbg\_105        & 13.0                    & 32.0                     & 68.0                  & 59.0                   & 0.54       & 1.75       & 170.0 & DD \\
bs006541        & 36.0                    & 65.0                     & 96.0                  & 83.0                   & 0.78        & 1.85       & 23.0 & DD \\
b012141\_012208 & 34.0                    & 93.0                     & 94.0                  & 63.0                   & 1.47       & 1.60       & 122.0 & RD \\
b15573          & 62.0                    & 81.0                     & 111.0                 & 84.0                   & 0.97        & 0.50       & 118.0 & DD \\
